\documentclass[11pt,a4paper]{article}

\usepackage[margin=1in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{fontspec}
\usepackage{xcolor}
\usepackage{titlesec}
\usepackage{ulem}
\usepackage{setspace}

% Set default font to sans-serif
\setmainfont{Liberation Sans}[
  BoldFont={Liberation Sans Bold},
  ItalicFont={Liberation Sans Italic},
  BoldItalicFont={Liberation Sans Bold Italic}
]

% Remove page numbers
\pagenumbering{gobble}

% Define a thicker underline command
\renewcommand{\ULthickness}{2pt} % Make underline thicker

% Style for section titles (bold with underline)
\titleformat{\section}
{\Large\bfseries}
{}
{0em}
{\uline}

\titlespacing{\section}{0pt}{12pt}{8pt}

% Custom list formatting with increased spacing between jobs
\setlist[itemize]{leftmargin=*,topsep=0pt,partopsep=0pt,parsep=0pt,itemsep=4pt}

% Define time period command with white text on black background
\newcommand{\timeperiod}[1]{%
    \hfill{\small\colorbox{black}{\textcolor{white}{\textbf{#1}}}}\par%
}

% Custom spacing
\setlength{\parindent}{0pt}
\setlength{\parskip}{0pt}

% Increase spacing between job entries
\newcommand{\jobsep}{\vspace{1.5em}}

\begin{document}

% Header (right-aligned)
\begin{flushright}
{\huge\textbf{Nikolai Dementev}}\\[4pt]
{\normalsize nidementyev@gmail.com | Moscow, Russia}
\end{flushright}

\section{EDUCATION}
\textbf{BS Thermal physics}\timeperiod{Sep 2011 - Jul 2016}
\textit{Moscow Power Engineering Institute, Moscow, Russia}

\section{EXPERIENCE}
\textbf{Data Engineer}\timeperiod{Nov 2020 - Present}
\textit{Delimobil, Moscow, Russia}
\begin{itemize}
    \item Engineered a comprehensive testing framework from scratch leveraging Python and Pytest, establishing robust data quality standards and maintaining a production-like testing environment
    \item Designed and implemented scalable ELT pipelines using Python, incorporating Anchor Modeling (6NF) techniques for optimized database architecture
    \item Orchestrated data integration across diverse sources including MySQL/PostgreSQL/MongoDB, Appsflyer, Mindbox, 1C, Google Sheets, Apache Kafka, and various REST APIs
    \item Developed a custom Domain-Specific Language (DSL) that streamlined pipeline development, reducing implementation time by 500% and improving code maintainability
    \item Architected and deployed a real-time data ingestion and analysis pipeline for dynamic pricing service across international markets, utilizing Apache Kafka and SingleStore DB
    \item Implemented CI/CD integration with GitLab CI/CD, automating deployment processes and reducing TTM by 50%
\end{itemize}

\jobsep
\textbf{QA Engineer (Automation)}\timeperiod{Feb 2019 - Nov 2020}
\textit{waves.tech (Blockchain platform), Moscow, Russia}
\begin{itemize}
    \item Automated integration testing of blockchain node application. Writing an API (REST/gRPC) for tests. Scala+Scalatest.
    \item Automated integration testing of smart contracts, written in RIDE, and the language itself. Scala+Scalatest.
    \item Developing custom transactions generator for load testing, implementation of load tests and integrating it with CI (Jenkins).
    \item Participation in development of Java/Python library for interacting with blockhain node via REST API.
\end{itemize}

\jobsep
\textbf{QA Engineer (Automation)}\timeperiod{Dec 2017 - Feb 2019}
\textit{Raiffeisen bank, Moscow, Russia}
\begin{itemize}
    \item Building a testing framework for card processing systems (REST/SOAP services, Oracle/Postgres DB, IBM MQ). Java+TestNG.
    \item Integration/unit tests writing.
    \item CI/CD integration (Atlassian Bamboo).
\end{itemize}

\jobsep
\textbf{QA Engineer (Automation)}\timeperiod{Apr 2017 - Dec 2017}
\textit{Mel.fm (Digital media platform), Moscow, Russia}
\begin{itemize}
    \item Automated integration/regression testing (Java+TestNG+Selenium).
    \item Load testing (Yandex Tank, Apache JMeter).
    \item Simple test environment management (Jenkins).
\end{itemize}

\section{SKILLS}
\begin{description}[labelwidth=1.5cm,leftmargin=!]
    \item[Languages] Java, Scala, Python
    \item[DBs] Oracle, MySQL, PostgreSQL, MemSQL (SingleStore), MongoDB, Vertica
    \item[MQs] IBM MQ, Apache Kafka
    \item[Schedulers] Airflow, Cron
    \item[Testing] Pytest, Scalatest, TestNG, JUnit
    \item[CI/CD tools] Jenkins, Atlassian Bamboo, Gitlab CI/CD tools
    \item[Other] Docker, AWS
\end{description}

\end{document}
